%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  \cventry
    {Technical University of Denmark} % Job title
    {Visiting PhD Student} % Organization
    {May 2022 – Present} % Location
    {Copenhagen - Denmark} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Cycling accident modelling using latent class choice models.}
        \item {Eye Tracker interviews on subjectivity of cycling risk.}
        \item {Supervised by Carlos Lima Azevedo (Machine Learning for Smart Mobility) and Felix Wilhelm Siebert (Transport Psychology)}
      \end{cvitems}
    }
    {
      \#ObjectiveCyclingSafety ~
      \#LatentClassChoiceModels ~
      \#SubjectiveCyclingSafety ~
      \#OnlineSurvey ~
      \#EyeTracker    
    }

%---------------------------------------------------------

  \cventry
    {Network of PhD candidates in urban mobility} % Job title
    {EIT Urban Mobility Doctoral Training Network} % Organization
    {Jun 2020 – Present} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Understanding how my research can be transformed with entreperneurship, innovation, and business.}
        \item {Platform for exchanging my research to fellow PhD candidates, senior resarchers, and practitioneers in urban mobility.}
      \end{cvitems}
    }
    {
      \#EuropeanInstituteOfInnovationAndTechnology ~
      \#DoctoralTrainingNetwork ~
      \#AcademiaIndustryCities ~
    }

%---------------------------------------------------------

  \cventry
    {Instituto Superior Técnico} % Job title
    {MIT Portugal Transportation System Doctoral Program} % Organization
    {Oct 2018 – Present} % Location
    {Lisbon - Portugal} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Framework for automatically and continuously understanding objective and subjective cycling safety.}
        \item {Supervised by Filipe Moura (IST), Manuel Marques (IST), and Carlos Lima Azevedo (DTU).}
        \item {Courses: Research Methodologies, Transport Demand Modelling, Infrastructure Optimization and Transport Operations, Statistical Learning, Nonlinear Optimization.}
      \end{cvitems}
    }
    {
      \#CyclingSafety ~
      \#ObjectiveSafety ~
      \#CyclingAccidentsDataset ~
      \#SubjectiveSafety ~
      \#PerceptionOfSafety ~
    }

%---------------------------------------------------------

  \cventry
    {Instituto Superior Técnico} % Job title
    {Integrated master’s in Electrical \& Computer Eng.} % Organization
    {Sep 2011 – May 2017} % Location
    {Lisbon - Portugal} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Master’s Thesis on: \underline{Video-Based Risk Assessment for Cyclists} supervised by Manuel Marques and João Paulo Costeira.}
      \end{cvitems}
    }
    {
      \#AndroidApp ~
      \#OpticalFlow ~
      \#FocusOfExpansion ~
      \#PerceptionOfRiskDescriptor ~
      \#Smartbike ~
    }

%---------------------------------------------------------

  \cventry
    {Universitá di Bologna} % Job title
    {Erasmus+ Exchange Program} % Organization
    {Sep 2015 – Feb 2016} % Location
    {Bologna - Italy} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Courses focused on entreperneurship, innovation, and computer vision.}
      \end{cvitems}
    }
    {
      \#AugmentedReality ~
      \#SudokuSolver ~
      \#ComputerVision ~
      \#Entreperneurship ~
    }

%---------------------------------------------------------
 
 
 
 
 
 
 
 
 
 
 
%---------------------------------------------------------
\end{cventries}
