%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Personal Project}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvhonors}

%---------------------------------------------------------
  \cvhonor
    {Restqa.io} % Position
    {Open Source End-to- End API testing platform that respects your data privacy \#OpenSource \#BDD  \#ATDD \#OpenApi \#Gherkin \#TestAutomation \#devops}
    {In service} % Location
    {2018} % Date(s)
  \cvhonor
    {atalent-consulting.com} % link
    {Business presentation website. \#Javascript \#mailchimp}
    {In service} % Location
    {2018} % Date(s)
  \cvhonor
    {gh-cv-assistant.olivierodo.me} % Position
    {A friendly Github bot that helps keeping your resume up to date. \#Gihub bot,\#NodeJs,\#Firebase, \#Docker}
    {Out of service} % Location
    {2018} % Date(s)
%---------------------------------------------------------
%  \cvhonor
%    {linassist.com} % Position
%    {Line bot connector (Line, slack, salesforce, NodeJs, mongoDb, docker)}
%    {In service} % Location
%    {2017} % Date(s)
%---------------------------------------------------------
  \cvhonor
    {Bolibot.io} % Position
    {Translation Slack bot.  \#Slack \#NodeJs \#googleApi \#Firebase \#Docker \#Heroku}
    {Out of service} % Location
    {2016} % Date(s)
%---------------------------------------------------------
  \cvhonor
    {Cookinky.com} % Position
    {Bio recipe sharing platform. \#Php \#Symfony \#RabbitMq \#NodeJs  \#Docker \#Aws \#Mysql \#ElasticSearch}
    {Out of service} % Location
    {2014} % Date(s)
%---------------------------------------------------------
  \cvhonor
    {Vaniadiary.com} % Position
    {HairDress salon managment tool. \#Php \#Symfony \#RabbitMq \#NodeJs \#Aws \#Mysql \#Ldap}
    {Out of service} % Location
    {2013} % Date(s)

%---------------------------------------------------------
\end{cvhonors}




%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Appointments}



  \cventry
    {Instituto Superior Técnico (IST), Universidade de Lisboa, Portugal} % Job title
    {PhD in Transportation Systems (MIT Portugal Program)} % Organization
    {Oct 2018 – Feb 2024} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\underline{Dissertation:} Objective and Subjective Safety Mapping for Urban Cyclists.}
        \item {Framework for automatically and continuously understanding objective and subjective cycling safety using authoritative and volunteered geographical information through a machine learning approach.}
        \item {Supervised by Filipe Moura (IST), Manuel Marques (IST), Carlos Lima Azevedo (DTU), and Felix Wilhelm Siebert (DTU)}
      \end{cvitems}
    }
    {
        \textit{Magma Cum Laude} (Pass with Distinction and Honor)
    }

  \cventryinner
    {Visiting PhD Student @ Technical University of Denmark} % Job title
    {May 2022 – Dec 2022} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Impact of built environment on cycling accidents using latent class discrete outcome models.}
        \item {Development of an image comparison framework for understanding subjective cycling safety.}
        \item {Analysis of perception of cycling safety using eye tracking.}
      \end{cvitems}
    }
    {
    }

  \cventryinner
    {EIT Urban Mobility Doctoral Training Network} % Job title
    {Jun 2020 – Feb 2024} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Platform for exchanging research to fellow PhD candidates, senior researchers, and practitioners in urban mobility.}
        \item {Understanding the value of my research through entrepreneurship, innovation, and business.}
      \end{cvitems}
    }
    {
    }

%---------------------------------------------------------

  \cventry
    {Instituto Superior Técnico, Universidade de Lisboa, Portugal} % Job title
    {Integrated MSc (BSc \& MSc) in Electrical \& Computer Engineering} % Organization
    {Sep 2011 – May 2017} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\underline{Dissertation:} Video-Based Risk Assessment for Cyclists.}
        \item {Framework for automatically and continuously understanding objective and subjective cycling safety using authoritative and volunteered geographical information through a machine learning approach.}
        \item {Supervised by Manuel Marques (IST), and João Paulo Costeira (IST).}
      \end{cvitems}
    }
    {
        Grade: 14/20
    }

  \cventryinner
    {Erasmus+ @ Universitá di Bologna, Italy} % Job title
    {Sep 2015 – Feb 2016} % Location
    {
    	\begin{cvitems} % Description(s) of tasks/responsibilities
    		\item {Coursework focused on entrepreneurship, innovation, and computer vision.}
    		\item {App development capable of reading sudoku games and solve them, displaying the final results using augmented reality.}
    	\end{cvitems}
    }
    { 	
    }
 
%---------------------------------------------------------